Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Fixed the table of numbers generator.

\begin{figure}[t]
\begin{center}
\includegraphics[width=3.2in]{church-relative-space.ps}
\includegraphics[width=3.2in]{church-relative-speed.ps}
\includegraphics[width=3.2in]{church-relative-time.ps}
\vspace{-1.5em}
\end{center}
\caption{Relative improvements over the baseline analyzer for the
  \Church{} benchmark in terms of peak memory usage, the rate of state
  transitions, and total analysis time. Each point is marked with the
  section that introduces the optimization.}
\label{fig:churchtime}
\end{figure}

@@

At each step during the initial development, we evaluate the
implementation on a benchmark from Vardoulakis and
Shivers~\cite{dvanhorn:Vardoulakis2011CFA2} that tests distributivity
of multiplication over addition on Church numerals.
%% \footnote{It is
%%   written here using Scheme notation and makes use of the shorthands:
%% %
%% \begin{alltt}
%%    (define (((f x) y) z) ...) \(\equiv\)
%%
%%    (define f (\(\lambda\) (x) (\(\lambda\) (y) (\(\lambda\) (z) ...))))
%% \end{alltt}
%%
%% \begin{alltt}
%%    \church{n} \(\equiv\) (\(\lambda\) (s) (\(\lambda\) (z) (s\(\subscript1\) (s\(\subscript2\) ... (s\(\subscript{n}\) z)))))
%% \end{alltt}}
The example, while small, is informative:
\begin{enumerate}
\item it can be written in most modern programming languages,
%
\item it was designed to stress an analyzer's ability to deal with
  complicated environment and control structure arising from the use
  of higher-order functions to encode arithmetic, and
%
\item it proves to be the \emph{least} improved benchmark of the
  complete suite considered in section~\ref{sec:eval}, and thus it
  serves as a good sanity check and lower-bound for each of the
  optimization techniques considered.
\end{enumerate}

@@

\begin{figure}
\begin{tabular}{@{}l|r|r|r|r|r|r|r@{}}
Program & LOC
& \multicolumn{2}{c|}{Time (ms)}
& \multicolumn{2}{c|}{Space (mb)}
& \multicolumn{2}{c@{}}{Speed (state/sec)}
\\
\hline\hline
nucleic &  3508 & 0 & 0 & 0 & 0 & 0 & 0\\
matrix  &  747  & ? & ? & ? & ? & ? & ?\\
nbody   & 1434  & ? & ? & ? & ? & ? & ?\\
earley  &  667  & ? & ? & ? & ? & ? & ?\\
maze    &  681  & ? & ? & ? & ? & ? & ?\\
church  &   41  & ? & ? & ? & ? & ? & ?\\
lattice &  214  & ? & ? & ? & ? & ? & ?\\
boyer   &  642  & ? & ? & ? & ? & ? & ?\\
mbrotz  &   68  & ? & ? & ? & ? & ? & ?
\end{tabular}
\caption{Overview performance comparison between baseline and
  optimized analyzer.}
\label{fig:bench-overview}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=3.2in]{church-relative-space.ps}
\includegraphics[width=3.2in]{church-relative-speed.ps}
\includegraphics[width=3.2in]{church-relative-time.ps}
\vspace{-1.5em}
\end{center}
\caption{Relative improvements over the baseline analyzer for the
  Vardoulakis and Shivers benchmark in terms of peak memory usage, the
  rate of state transitions, and total analysis time.}
\label{fig:churchtime}
\end{figure}

@@

At each step during the initial development, we evaluate the
implementation on an example, shown in figure~\ref{fig:church}, taken
from the flow analysis literature~\cite{dvanhorn:Vardoulakis2011CFA2}
that tests distributivity of multiplication over addition on Church
numerals.
%% \footnote{It is
%%   written here using Scheme notation and makes use of the shorthands:
%% %
%% \begin{alltt}
%%    (define (((f x) y) z) ...) \(\equiv\)
%%
%%    (define f (\(\lambda\) (x) (\(\lambda\) (y) (\(\lambda\) (z) ...))))
%% \end{alltt}
%%
%% \begin{alltt}
%%    \church{n} \(\equiv\) (\(\lambda\) (s) (\(\lambda\) (z) (s\(\subscript1\) (s\(\subscript2\) ... (s\(\subscript{n}\) z)))))
%% \end{alltt}}
The example, while small, is informative:
\begin{enumerate}
\item it can be written in most modern programming languages,
%
\item it was designed to stress an analyzer's ability to deal with
  complicated environment and control structure arising from the use
  of higher-order functions to encode arithmetic, and
%
\item it proves to be the \emph{least} improved benchmark of the
  complete suite considered in section~\ref{sec:eval}, and thus it
  serves as a good sanity check and lower-bound for each of the
  optimization techniques considered.
\end{enumerate}

@@

\begin{figure}
\include{bench-overview}
\caption{Overview performance comparison between baseline and
  optimized analyzer.}
\label{fig:bench-overview}
\end{figure}
